---
title: "BiscuiteerData User Guide"
data: "`r BiocStyle::doc_date()`"
package: "`r BiocStyle::pkg_ver('biscuiteerData')`"
output:
  BiocStyle::html_document:
    highlight: pygments
    toc_float: true
    fig_width: 8
    fig_height: 6
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Biscuiteer User Guide}
  %\VignetteEncoding[utf8]{inputenc}
---

# BiscuiteerData

`biscuiteerData` is a complementary package to the Bioconductor package
`biscuiteer`. It contains a handful of datasets to be used when running
functions in `biscuiteer`.

# Quick Start

## Installing

From Bioconductor,
```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")
BiocManager::install("biscuiteerData")
```

A development version is available on GitHub and can be installed via:
```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")
BiocManager::install("trichelab/biscuiteerData")
```

# Usage

`biscuiteerData` data is accessible using the `biscuiteerDataGet` function:
```{r, eval=FALSE}
library(biscuiteerData)
PMDs.hg19 <- biscuiteerDataGet("PMDs.hg19")
```

A list of the titles for the available data can be retrieved via:
```{r, eval=FALSE}
biscuiteerDataList()
```

A list of all versions (where the versions are the dates uploaded) is produced
via:
```{r, eval=FALSE}
biscuiteerDataListDates()
```

An older version of the data can be retrieved using the `dateAdded` argument of
`biscuiteerDataGet`:
```{r, eval=FALSE}
PMDs.hg19 <- biscuiteerDataGet("PMDs.hg19", dateAdded = "OLD-DATE")
```
